$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-03-31 paper/e6ssm-tuning-paper.tex
Added missing space before citation

There is another limit which plays a similar role.  Chargino limits
directly constrain the $\mu$ parameter (or effective $\mu$ parameter
in these $U(1)$ extensions).  However the chargino limits from the LHC
depend on whether there are light sleptons or sneutrinos and the mass
difference between the lightest chargino and lightest neutralino.
Current limits placed by CMS and ATLAS extend up to
$m_{\tilde{\chi}^\pm_1} \approx 700-740$ GeV if there are light
sleptons\cite{Khachatryan:2014qwa, Aad:2014nua} with much weaker
bounds if there are no light sleptons or sneutrinos\footnote{Useful
  summary plots of these limit may be found on the public pages of
  ATLAS,
  \url{https://atlas.web.cern.ch/Atlas/GROUPS/PHYSICS/CombinedSummaryPlots/SUSY/ATLAS_SUSY_EWSummary/ATLAS_SUSY_EWSummary.png}
  and CMS
  \url{http://cms.web.cern.ch/sites/cms.web.cern.ch/files/styles/large/public/field/image/Image_03_exclusion_Combined.png?itok=8FMBpu_1}.}.

>>>>

There is another limit which plays a similar role.  Chargino limits
directly constrain the $\mu$ parameter (or effective $\mu$ parameter
in these $U(1)$ extensions).  However the chargino limits from the LHC
depend on whether there are light sleptons or sneutrinos and the mass
difference between the lightest chargino and lightest neutralino.
Current limits placed by CMS and ATLAS extend up to
$m_{\tilde{\chi}^\pm_1} \approx 700-740$ GeV if there are light
sleptons \cite{Khachatryan:2014qwa, Aad:2014nua} with much weaker
bounds if there are no light sleptons or sneutrinos\footnote{Useful
  summary plots of these limit may be found on the public pages of
  ATLAS,
  \url{https://atlas.web.cern.ch/Atlas/GROUPS/PHYSICS/CombinedSummaryPlots/SUSY/ATLAS_SUSY_EWSummary/ATLAS_SUSY_EWSummary.png}
  and CMS
  \url{http://cms.web.cern.ch/sites/cms.web.cern.ch/files/styles/large/public/field/image/Image_03_exclusion_Combined.png?itok=8FMBpu_1}.}.
